Constant Error Tolerance Computational Fuzzy Extractors

### 2014-02-03 trunk/constantRate/ConstCompFuzzExt.tex

Unfortunately, fuzzy extractors have not yielded key derivation for all noisy sources.
This is because there is tension between security and error-tolerance.  The key should be uniform to an observer but nearby $w'$ should map to the same key.  By nearby, we mean that $\dis(w, w')\leq t$ for some metric $\dis$.  In the information-theoretic realm, increasing $t$ means a decrease in the strength of the key $r$.  This is because a fuzzy extractor can be converted into an error correcting code~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.  The length of $r$ is dictated by size of the best code that corrects $t$ errors.  Error-correcting codes are well studied and we have tight bounds on this quantity. % how many codewords may be in a code that corrects $t$ errors.

\bnote{the whole introduction should be rewritten, doesn't mention second construction.}
We consider the Hamming metric.  For the Hamming metric, the key may be no longer than the difference between the starting entropy of the source\footnote{We assume that the fuzzy extractor operates independently of the source $W$.  As we discuss later, it is possible to avoid these losses if the fuzzy extractor knows something about the distribution.} and logarithm of the number of error patterns to be corrected. For the remainder of this paper we denote this quantity by $gap$.  This represents a real problem, important biometrics, such as irises~\cite{daugman2004}, have $gap <0$ and current fuzzy extractors provide no security guarantee.

@@

This does not need to be the case in the computational setting.  Fuller, Meng, and Reyzin define computational fuzzy extractors~\cite{fuller2013computational}.  Computational fuzzy extractors produce pseudorandom instead of truly random keys.  They hypothesize a computational fuzzy extractor may exist with a small or negative $gap$.  We resolve this question and construct a computational fuzzy extractor when $gap<0$.  This is impossible for an arbitrary min-entropy distribution as every point could be within distance $t$.  A necessary condition for security is that a negligible portion of the source's probability distribution lies within any Hamming ball of radius $t$.  We require a stronger condition that many blocks are unpredictable~(\defref{def:block guessable}).

The goal of an information-theoretic fuzzy extractor is to output a maximal length key for a source $W$.
In the computational setting, a key may be expanded once it is long enough to serve as input to a pseudorandom generator.  Our focus is on expanding the class of distributions for which we can provide meaningful security.

\bnote{two constructions}
\textbf{Overview of Construction:}  Fuller, Meng, and Reyzin~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational} show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful.  Instead, the authors suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent high-entropy secret instead of recovering $w$.  This is known as a fuzzy conductor~(the entropy is ``conducted'' from $w$ to a new distribution) and was introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}.  Here, we follow the second approach and use a \emph{computational} fuzzy conductor.

Our construction~(\consref{cons:first construction}) is based on obfuscation of point programs.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.  For a point program, this means hiding all partial information about the point $w$.  Obfuscation for this class of functions is achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.

Consider a source $W = W_1,..., W_\ell$ that is split into blocks~(over a large alphabet).  We would like to tolerate errors in $t$ individual blocks.  For each block $i$, we flip a coin $c_i$ and either obfuscate $I_{w_i}$ or pick a random point $r_i$ and obfuscate $I_{r_i}$.  This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.  With a close value $w'$, $\rec$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.  For most locations $i$, \rep can determine whether $w_i$ or a random value was the point obfuscated.  Thus, most bits of $c_i$ are recoverable. To tolerate errors we choose the coins $c$ from an error-correcting code.  The set of possible codewords forms a high entropy distribution.  This construction conducts entropy from $w$ to $c$ and is a computational fuzzy conductor.  It may be converted to a computational fuzzy extractor by either information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors.  It is hard to recover $w$ from the value $c$.   This is necessary to overcome lower bounds on entropy loss~\cite[Section 3.3]{fuller2013computational}.
Our construction is inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.

Our construction provides several advantages over previous constructions of computational fuzzy extractors:
\begin{itemize}
\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions.\footnote{There are examples where no loss is necessary in a fuzzy extractor.  If $W$ consists of points from an error-correcting code of sufficient minimum distance, then no public information is necessary and $gap$ may be negative.  This is not in the spirit of a fuzzy extractor as the distribution is already ``error-corrected.''  For arbitrary min-entropy sources, analysis of information-theoretic fuzzy extractors proceeds by arguing an adversary learns at most a bit for each bit necessary for error correction.   For an arbitrary distribution, this is at least the logarithm of the total number of error patterns.  The distributions supported by our construction are not error-correcting codes, we require unpredictability in many dimensions~(see \defref{def:block guessable}).}
\item The first computational fuzzy extractor that allows for a constant fraction of errors.  Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
\item The first computational fuzzy extractor where blocks are not required to be uniformly distributed.  Our construction simply requires a large number of blocks that are unguessable given equality queries.  This subsumes the distributions supported by~\cite[Construction 4.1]{fuller2013computational}.
\end{itemize}
\bnote{compare contrast constructions}

\textbf{Limitations: } The main limitation of our construction is that each block is individually obfuscated.  This means that blocks much be drawn from distributions with super-logarithmic entropy.  Furthermore, our distance is Hamming distance over a large alphabet~(super-polynomial in the security parameter).  Our construction is applicable for physical sources where many bits are expected to err consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).  Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.

\textbf{Connection with Noisy Point Obfuscation: } Ideally, our construction would be a noisy point obfuscation~(which is a stronger object than a computational fuzzy extractor).  Unfortunately, this is not the case.  Each block is individually obfuscated, so an adversary may ask equality queries on individual blocks.  If not all blocks have high entropy an adversary may learn significant information about the source.  Thus, our construction is not a obfuscation for any reasonable definition.  Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $gap>>0$ using a information-reconciliation component that hides partial information.  Constructing VBB obfuscation for sources where $gap <0$ is an open problem.
\bnote{does second construction get closer to obfuscation?}

The remainder is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries} , describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.

@@

\begin{lemma}
\label{lem:correct of cons}
Let $C$ be a $(\neigh_t, \delta_{code})$-code.  Then when $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then
\[
\Pr[\rep( w', P) = R] \geq 1-\left(\frac{\ell}{2^n}+\delta_{code}\right).
\]
That is, \consref{cons:first construction} is correct with error at most $\ell/2^n+\delta_{code}$.
\end{lemma}

\textbf{Note: }By using a more structured type of code, the necessary error tolerance may be decreased from $t$ to  $(1/2+O(1))t$ by arguing that roughly half of the mismatches between $w, w'$ occur where $c_i =1$.  However, this requires a codeword where most codewords have Hamming weight close to $1/2$.

@@

\begin{corollary}
Let $\eta = \omega(\log n)$ and let $C\subset\zo^\ell$ be a $(\neigh_t, \delta_{code})$ for $t' = \Theta(\ell)$ and $\delta_{code} = \ngl(n)$.  Then when
\[
\dis(w, w')= \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = O(\frac{\gamma-\eta}{\eta}) = O(\gamma/\eta)
\]
and $(R, P)\leftarrow \gen(w)$, then
\[
\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n} - O(2^{-\eta}) -\delta_{code}= 1-\ngl(n).
\]
That is, \consref{cons:sampling} is correct with overwhelming probability.

\end{corollary}
\subsection{Discussion of \consref{cons:sampling}}
\consref{cons:sampling} achieves $gap<0$ for an interesting setting of parameters.  The required entropy of  an unordered block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.  We are able to correct $O(\gamma/\eta)$ errors.
This yields:
\begin{align*}
gap &= \Hoo(W) -\log |B_t| \\
&< \Theta(\gamma)- t \log |\mathcal{Z}|\\
&= \Theta(\gamma) - O(\gamma/\eta) \log |\mathcal{Z}|\\
\end{align*}
That is, \consref{cons:sampling} achieves $gap<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$.  If we are willing to accept $gap\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.  However, in this setting $gap =\Omega(\gamma)$ and known constructions of information-theoretic fuzzy extractors suffice in this setting.
\bibliographystyle{alpha}
\bibliography{crypto}

@@

>>>>

Unfortunately, fuzzy extractors have not yielded key derivation for all noisy sources.
This is because there is tension between security and error-tolerance.  The key should be uniform to an observer but nearby $w'$ should map to the same key.  By nearby, we mean that $\dis(w, w')\leq t$ for some metric $\dis$.  In the information-theoretic realm, increasing $t$ means a decrease in the strength of the key $r$.  This is because a fuzzy extractor can be converted into an error correcting code~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.  The length of the key $r$ is dictated by size of the best code that corrects $t$ errors.  Error-correcting codes are well studied and we have tight bounds on this quantity. % how many codewords may be in a code that corrects $t$ errors.

We consider the Hamming metric.  For the Hamming metric, there exists a distribution $W$ where the key derived from $W$ may be no longer than the difference between the starting entropy of the source and logarithm of the number of error patterns to be corrected. For the remainder of this paper we denote this quantity by $gap$.  This represents a real problem as $gap<0$ for important biometrics and current fuzzy extractors provide no security guarantee~(see \apref{sec:iris no key}).

@@

To achieve security when $gap<0$, some restriction on the source distribution $W$ is necessary~(minimal conditions are discussed in~\apref{sec:minimal conditions}).  However, the tools for constructing information-theoretic fuzzy extractors have not admitted natural and meaningful restrictions.  Fuller, Meng, and Reyzin define a computationally-secure version of fuzzy extractors~\cite{fuller2013computational}.  Computational fuzzy extractors produce pseudorandom instead of truly random keys.  Building a computational fuzzy extractor with $gap<0$ may be possible for a broader class of distributions than is possible in the information-theoretic realm.

In this work, we show that constructing a computational fuzzy extractor is possible for a large class of distributions with $gap<0$.
%We resolve this question and construct a computational fuzzy extractor when $gap<0$.  This is impossible for an arbitrary min-entropy distribution as every point could be within distance $t$.  A necessary condition for security is that a negligible portion of the source's probability distribution lies within any Hamming ball of radius $t$.  We require a stronger condition that many blocks are unpredictable~(\defref{def:block guessable}).
%The goal of an information-theoretic fuzzy extractor is to output a maximal length key for a source $W$.
In the computational setting, a key may be expanded once it is long enough to serve as input to a pseudorandom generator.  We focus on providing a reasonable length key when $gap<0$.
Fuller, Meng, and Reyzin show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.  Instead, the authors suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent high-entropy secret instead of recovering $w$.  This is known as a fuzzy conductor~(the entropy is ``conducted'' from $w$ to a new distribution) and was introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}.  Here, we follow the second approach and use a \emph{computational} fuzzy conductor.  We present two constructions of computational fuzzy conductors for different types of source distributions $W$.  These constructions may be converted to a computational fuzzy extractor by either information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).

Both of constructions are based on the obfuscation of point programs.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.  For a point program, this means hiding all partial information about the point $w$.  Obfuscation for this class of functions is achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.  Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.

\textbf{\consref{cons:first construction}: }
Consider a source $W = W_1,..., W_\ell$ that is split into blocks~(over a large alphabet).  We would like to tolerate errors in $t$ individual blocks.  For each block $i$, we flip a coin $c_i$ and either obfuscate $I_{w_i}$ or pick a random point $r_i$ and obfuscate $I_{r_i}$.  This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.  With a close value $w'$, $\rec$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.  For most locations $i$, \rep can determine whether $w_i$ or a random value was the point obfuscated.  Thus, most bits of $c_i$ are recoverable. To tolerate errors we choose the coins $c$ from an error-correcting code.  The set of possible codewords forms a high entropy distribution.  This construction conducts entropy from $w$ to $c$ and is a computational fuzzy conductor.

In \consref{cons:first construction}, each block of $W$ is individually obfuscated.  This has two drawbacks, first an adversary may learn the value of some blocks which may be sensitive information.  Second, security only holds for sources where a large number of blocks have super-logarithmic entropy~(\defref{def:block guessable}).  Our second construction addresses these problems.

\textbf{\consref{cons:sampling}: }
As before we consider a source $W=W_1,...,W_\ell$ that is split into blocks.  However, instead of obfuscating individually
blocks individually, for each bit $c_i$ we randomly select a subset of blocks.  These blocks are concatenated and obfuscated together.  By sampling, we can significantly decrease the entropy requirement on individual blocks.  This paradigm is similar to the \emph{sample-then-extract} paradigm in the locally-computable extractor literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason, we call \consref{cons:sampling} \emph{sample-then-obfuscate}.

%Our construction provides several advantages over previous constructions of computational fuzzy extractors:
%\begin{itemize}
%\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions.\item The first computational fuzzy extractor that allows for a constant fraction of errors.  Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
%\item The first computational fuzzy extractor where blocks are not required to be uniformly distributed.  Our construction simply requires a large number of blocks that are unguessable given equality queries.  This subsumes the distributions supported by~\cite[Construction 4.1]{fuller2013computational}.
%\end{itemize}

\textbf{Limitations: } In order to achieve security with $gap<0$, our alphabet~(for Hamming distance) must be super-polynomial in the security parameter.  Our constructions are applicable for sources where many bits are expected to err consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).  Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.  Furthermore, we may leak sensitive information about the underlying source $W$.  For example, in \consref{cons:first construction} it is possible to learn the value of individual blocks $W_i$.  Our two constructions are not noisy point obfuscation for any reasonable definition of obfuscation.  Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $gap>>0$ using a information-reconciliation component that hides all partial information.  Constructing VBB obfuscation for sources where $gap <0$ is an open problem.

The remainder of this paper is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries}, describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, and present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.

@@

\begin{lemma}
\label{lem:correct of cons}
Let $C$ be a $(\neigh_t, \delta_{code})$-code.  When $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$
\[
\Pr[\rep( w', P) = R] \geq 1-\left(\frac{\ell}{2^n}+\delta_{code}\right).
\]
That is, \consref{cons:first construction} is correct with error at most $\ell/2^n+\delta_{code}$.
\end{lemma}

\textbf{Note: }By using a more structured type of code, the necessary error tolerance may be decreased from $t$ to  $(1/2+O(1))t$ by arguing that roughly half of the mismatches between $w, w'$ occur where $c_i =1$.  This requires a code where most codewords have Hamming weight close to $1/2$.

@@

\begin{corollary}
Let $\eta = \omega(\log n)$ and let $C\subset\zo^\ell$ be a $(\neigh_t, \delta_{code})$ for $t' = \Theta(\ell)$ and $\delta_{code} = \ngl(n)$.  Then when
\[
\dis(w, w')= \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = \Theta(\frac{\gamma-\eta}{\eta}) = \Theta(\gamma/\eta)
\]
and $(R, P)\leftarrow \gen(w)$, then
\[
\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n} - O(2^{-\eta}) -\delta_{code}= 1-\ngl(n).
\]
That is, \consref{cons:sampling} is correct with overwhelming probability.

\end{corollary}
\subsection{Discussion of \consref{cons:sampling}}
\consref{cons:sampling} achieves $gap<0$ for an interesting setting of parameters.  The required entropy of  an unordered block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.  We are able to correct $O(\gamma/\eta)$ errors.
This yields:
\begin{align*}
gap &= \Hoo(W) -\log |B_t| \\
&< \Theta(\gamma)- t \log |\mathcal{Z}|\\
&= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|\\
\end{align*}
That is, \consref{cons:sampling} achieves $gap<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$.  If we are willing to accept $gap\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.  However, in this setting $gap =\Omega(\gamma)$ and known constructions of information-theoretic fuzzy extractors suffice in this setting.
\bibliographystyle{alpha}
\bibliography{crypto}

@@

\section{$gap<0$ for Irises}
\label{sec:iris no key}
The iris is the biometric believed to have the most entropy.  The best estimate for iris entropy is $250$ bits~\cite{daugman2004}.  Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.  The transform computes a phase angle at $1024$ locations, this angle is then quantized into a positive/negative value in the two dimensions.  This transform is designed for the process of identification, achieving the best possible true accept/false accept tradeoff.

The precise number of errors that must be tolerated depends on the desired true accept rate (how often the correct key is produced).  For a true accept rate of $20\%$, a $t$ of approximately $205$ is required.\footnote{Daugman considerably improves his true accept rate using a masking vector, where bits that are not considered ``trustworthy'' are excluded from the comparison.  The comparison between the two readings is then made using bits not excluded by either image.  It is not clear how to extend into the fuzzy extractor setting.}  We have the following calculation for $gap$:
\begin{align*}
gap &= \Hoo(W) - \log |B_t|\\
&= 249 - \log \sum_{i=0}^{205} {2048 \choose i} = -707.
\end{align*}
Irises are believed to be the strongest biometric and reliable key derivation from irises is an open problem.
